### 2016-08-19 analysis-note-v2/RTPC.tex
updating the RTPC, ch5 and the appendix for the analysis note

\subsubsection{RTPC good track requirements}

@@

\begin{equation}
   \chi^{2} = \frac{\displaystyle \left(\frac{DOCA}{\sigma_r}\right)^2 
       + \sum_{i = 1}^{ N_{pts}} \left(\frac{r^{pt}_{i} 
      - r^{helix}_{i} }{\sigma_{r}}\right)^{2}  + \left( \frac{\phi^{pt}_{i} - 
      \phi^{helix}_{i} }{\sigma_{\phi}}\right)^{2} + \left( \frac{z^{pt}_{i} - 
   z^{helix}_{i} }{\sigma_{z} } \right)^{2}}{N_{pts} - 4}
\end{equation}
where $\frac{DOCA}{\sigma_r}$ is the beam-spot constraint, $r^{pt}_{i}$, 
$\phi^{pt}_{i}$, $z^{pt}_{i}$ are the radial, azimuthal, longitudinal 
coordinates of each reconstructed hit "$i$". ($r^{helix}_{i}$,
$\phi^{helix}_{i}$, $z^{helix}_{i}$) is the point on the helix fit that is 
closest to the reconstructed hit $i$. The resolutions are defined as ($\sigma_{r}$, 
$\sigma_{\phi}$, $\sigma_{z}$) = (0.53 mm, 2$^{\circ}$, 1.2 mm) based on the size
of the readout pads were kept identical for all calibration iterations. 
$N_{pts}$ is the total number of the hits in the chain.  Figure 
\ref{fig:rrtpc_X2} shows the $\chi^{2}$ distributions for the positive tracks 
which originate within the RTPC.

@@

\item $sdist$ ($\in$ [-2.0,2.0] mm) and $edist$ ($\in$ [-1,5] mm ) cuts: the cuts are applied to ensure that a track is on time, i.e. that the first ionization point is close to the cathode and the last point is close to the anode. The $sdist$ and $edist$ distributions are shown in figures \ref{fig:rrtpc_sdist} and \ref{fig:rrtpc_edist} respectively\footnote{The long tail on the positive side of the $edist$ distribution is mostly due to electronic noise. Note that after applying all the elastic He-4 selection cuts, we observe that most of the tails for both $edist$ and $sdist$ are removed.}.

@@

>>>>

\subsubsection{RTPC good track requirements} \label{good_track_req}

@@

\begin{equation}
   \chi^{2} = \frac{\displaystyle \left(\frac{DOCA}{\sigma_r}\right)^2 
       + \sum_{i = 1}^{ N_{pts}} \left(\frac{r^{pt}_{i} 
      - r^{helix}_{i} }{\sigma_{r}}\right)^{2}  + \left( \frac{\phi^{pt}_{i} - 
      \phi^{helix}_{i} }{\sigma_{\phi}}\right)^{2} + \left( \frac{z^{pt}_{i} - 
   z^{helix}_{i} }{\sigma_{z} } \right)^{2}}{N_{pts} - 4}
\end{equation}
where $\frac{DOCA}{\sigma_r}$ is the beam-spot constraint, $r^{pt}_{i}$, 
$\phi^{pt}_{i}$, $z^{pt}_{i}$ are the radial, azimuthal, longitudinal 
coordinates of each reconstructed hit "$i$". ($r^{helix}_{i}$,
$\phi^{helix}_{i}$, $z^{helix}_{i}$) is the point on the helix fit that is 
closest, in Euclidean (3D) space, to the reconstructed hit $i$. The resolutions 
are defined as ($\sigma_{r}$, $\sigma_{\phi}$, $\sigma_{z}$) = (0.53 mm, 
2$^{\circ}$, 1.2 mm) based on the size
of the readout pads were kept identical for all calibration iterations. These 
resolutions were derived by CLAS-BoNus experiment \cite{BONUS}. $N_{pts}$ is 
the total number of the hits in the chain.  Figure \ref{fig:rrtpc_X2} shows the 
$\chi^{2}$ distributions for the positive tracks which originate within the 
RTPC.

@@

\item $sdist$ ($\in$ [-2.0,2.0] mm) and $edist$ ($\in$ [-1,5] mm ) cuts: the 
   cuts are applied to ensure that a track is on time, i.e. the first 
   ionization point is close to the cathode and the last point is close to the 
   anode. For both $sdist$ and $edist$, positive values correspond to tracking 
   points inside the drift region, while negatives are outside the drift 
   region. So, in terms of the path length of the track starting from the 
   vertex, $sdist$ and $edist$ have opposite signs. The $sdist$ and $edist$ 
   distributions are shown in figures \ref{fig:rrtpc_sdist} and 
   \ref{fig:rrtpc_edist} respectively\footnote{The long tail on the positive 
      side of the $edist$ distribution is mostly due to electronic noise.  Note 
      that after applying all the elastic He-4 selection cuts, we observe that 
   most of the tails for both $edist$ and $sdist$ are removed.}.

@@

\subsubsection{Checking the initial good track requirements}
~~~~In this section, we recheck the individual good track requirements 
presented in section \ref{good_track_req}, where we apply the other good track 
and elastic requirements and watch the individual variables.

Figure \ref{fig:2-z-vertex} presents the z-vertex distributions of the elastic 
events, where all the good track and elastic requirements were applied. One 
sees that the initial [-80:80] mm cuts on the helium z-vertex appear to be 
suitable cuts to ensure that the reconstructed tracks are within the physical 
volume of the RTPC.
\begin{figure}[tp]
  \centering
   \includegraphics[scale=0.34]{fig_rtpc/updates/elastic_z_vertex.png}
\caption{z-vertex distributions for the electrons of the identified elastic 
events in the two modules of the RTPC.}
\label{fig:2-z-vertex}
\end{figure}

In figure \ref{fig:2-r0}, we show the distribution of the radius of curvature 
for the identified elastic tracks in the RTPC. One sees that applying the other 
good track and elastic conditions will eliminate all the negative tracks and 
the tracks with $r_{0}$ less than 30 mm.
\begin{figure}[tp]
   \centering
\includegraphics[scale=0.34]{fig_rtpc/updates/r0_elastic_1p2GeV.png}
\caption{The radius of curvature distributions of the identified elastic 
$^{4}$He tracks in the two modules of the RTPC after applying the other good 
track and elastic events}.
\label{fig:2-r0}
\end{figure}

The distributions of $sdist$ and $edist$ for the identified elastic $^4$He 
elastic tracks, figure \ref{fig:2-sdist-edist}, show that most of the tails, 
which are mostly due to electronic noise, are removed. Therefore, making 
tighter cuts would not cause changes in the calibration as the tracks in the 
tail regions are cleaned by the other good track and elastic cuts.

\begin{figure}[tp]
\includegraphics[scale=0.34]{fig_rtpc/updates/sdist_elastic_1p2GeV.png}
\includegraphics[scale=0.34]{fig_rtpc/updates/edist_elastic_1p2GeV.png}
\caption{ $sdist$ (on left) and $edist$ (on right) distributions for the 
identified $^4$He elastic tracks in the two modules of the RTPC after applying 
the other cuts. The vertical dashed red lines indicate the initial cuts were 
applied to select the good tracks.}
\label{fig:2-sdist-edist}
\end{figure}

### 2016-08-19 analysis-note-v2/results.tex
updating the RTPC, ch5 and the appendix for the analysis note

\begin{figure}[tpb]
\centering
\vspace{-0.2in}
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_Q2_90.pdf} \\
\vspace{-0.1in}
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_xB_90.pdf}\\ 
\vspace{-0.1in}
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_t_90.pdf} \caption{The 
   $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of the 
   incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle panel: 
   the red and the blue curves are theoretical calculations from 
   \cite{simonetta_2}. On the bottom: the green circles are the HERMES 
   $-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
   the colored curves represent theoretical calculations from 
\cite{simonetta_2}.  } \label{fig:incoh_Q2_xB_t_ALU}
\end{figure}

@@

\section{Generalized EMC ratios}
~~~~Comparing our measured DVCS channels to the free-proton DVCS reaction 
allows us to investigate the nuclear medium effects at the GPD level. For this 
we use analyzes performed on free-proton with the DVCS data sets taken by the CLAS 
collaboration, during the E1-DVCS experiment (parts 1 and 2). The results of 
part 1 are already published \cite{FX_BSA, CLAS_cross_section}. Herein, our 
coherent and incoherent beam-spin asymmetries are compared to the results of
free proton asymmetries from this publication.

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.38]{fig_updated/BSA_ratio_coh_Q2.pdf}\\
\includegraphics[scale=0.38]{fig_updated/BSA_ratio_coh_xB.pdf}\\
\includegraphics[scale=0.38]{fig_updated/BSA_ratio_coh_t.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
$\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
middle), and $t$ (on the bottom). The black squares are our results, the 
green circles are the HERMES inclusive measurement \cite{HERMES_BSA} results. 
The blue and red curves are from an on-shell calculations from S. Liuti and K. Taneja 
\cite{simonetta_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.37]{fig_updated/BSA_ratio_incoh_Q2.pdf}\\
\includegraphics[scale=0.37]{fig_updated/BSA_ratio_incoh_xB.pdf}\\
\includegraphics[scale=0.37]{fig_updated/BSA_ratio_incoh_t.pdf}
\caption{The $A_{LU}$ ratio between $^4$He and free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $-t$ (on the bottom). The black squares represent the results of 
   this work and the green circles are the HERMES measurements 
   \cite{HERMES_BSA}. These measurements are compared to theoretical 
   predictions from S. Liuti and K. Taneja \cite{simonetta_2}, the red and the 
blue curves, and the model predictions from V. Guzey et al. based on the 
off-shell calculations \cite{EMC_vadim_4}, in black, purple and brown dashed 
curves.}
\label{fig:coh_EMC_ratio_ALU}
\end{figure}
~\\

>>>>

\begin{figure}[tpb]
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_Q2_90.pdf} 
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_xB_90.pdf}
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_t_90.pdf} 
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of 
   the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle 
   panel: the red and the blue curves are theoretical calculations from 
   \cite{simonetta_2}. On the bottom: the green circles are the HERMES 
$-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
the colored curves represent theoretical calculations from \cite{simonetta_2}.  
} \label{fig:incoh_Q2_xB_t_ALU}
\end{figure}

@@

\section{Generalized EMC ratios} \label{sec:Generalized_EMC}
~~~~Comparing our measured DVCS channels to the free-proton DVCS reaction 
allows us to investigate the nuclear medium effects at the GPD level. For this 
we use analyzes performed on free-proton with the DVCS data sets taken by the CLAS 
collaboration, during the E1-DVCS experiment (parts 1 and 2). The results of 
part 1 are already published \cite{FX_BSA, CLAS_cross_section}. Herein, our 
coherent and incoherent beam-spin asymmetries are compared to the results of
free proton asymmetries from this publication.

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.38]{fig_updated/BSA_ratio_incoh_Q2.pdf}\\
\includegraphics[scale=0.38]{fig_updated/BSA_ratio_incoh_xB.pdf}\\
\includegraphics[scale=0.38]{fig_updated/BSA_ratio_incoh_t.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $t$ (on the bottom). The black squares are our results, the 
   green circles are the HERMES inclusive measurement \cite{HERMES_BSA} 
   results.  The blue and red curves are from an on-shell calculations from S. 
Liuti and K. Taneja \cite{simonetta_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.37]{fig_updated/BSA_ratio_coh_Q2.pdf}\\
\includegraphics[scale=0.37]{fig_updated/BSA_ratio_coh_xB.pdf}\\
\includegraphics[scale=0.37]{fig_updated/BSA_ratio_coh_t.pdf}
\caption{The $A_{LU}$ ratio between $^4$He and free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $-t$ (on the bottom). The black squares represent the results of 
   this work and the green circles are the HERMES measurements 
   \cite{HERMES_BSA}. These measurements are compared to theoretical 
   predictions from S. Liuti and K. Taneja \cite{simonetta_2}, the red and the 
blue curves, and the model predictions from V. Guzey et al. based on the 
off-shell calculations \cite{EMC_vadim_4}, in black, purple and brown dashed 
curves.}
\label{fig:coh_EMC_ratio_ALU}
\end{figure}
~\\
